---
title: "belief_AltMotives - study 2" 
author: Ryan Carlson
output: html_document
---
```{r install/load packages,include=FALSE}

library("plyr") # plyr for aggregate data
library("tidyverse")
library("ggm") # for partial correlations
library("ppcor") # " "
library("psych") # for trait measures
library("lsr") # for computing effect sizes
library("devtools") #pirateplots
library("yarrr")#pirateplots
library("rstudioapi")
library("broom")
library("weights")

```

```{r set directory, read in data set, include=FALSE}

#Set working directory to the location of this R file (note: the dataset should be in the same folder)
  # curr_dir <- getActiveDocumentContext()$path # get path to currently open R file
  # setwd(dirname(curr_dir)) # set the working directory to curr_dirr
  # #print(getwd()) # print directory
  # rm("curr_dir")
  
```

```{r read in raw data set, include=FALSE}

df = read.csv('bAM_s2_data.csv') #raw data frame 
data = df[,c("id","condition")] # a new, clean data frame 

```

```{r knit functions,echo=FALSE}
  
#formatting p-values for APA
format_pval <- function(x){
  if (x < .001) return(paste('<', '.001'))
  if (x > .1) return(paste('=', rd(x, 2)))
  paste('=', rd(x, 3))   # 3 = no. of digits to round p value to if p < .001 
}

#function for removing NAs from a specific column
reduceFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

```

```{r create clean data frame for analysis, include=FALSE}

#create averages for perception ratings 

#AVG: altruism ratings
  alt = df[,grep("Alt", names(df))] #get all altruism ratings 
  #DF should contain ncol = 216. Or N = 3 (DVs per V) x 8 (Vs) x 4 (orders) x 2 (cond: motive/outcome) + 3 (DVs per control V) x 8 (Vs)
    #ncol(alt) #sanity check
  alt = alt %>% mutate(alt_avg=rowMeans(alt, na.rm = TRUE)) #create new column averaging across them
  data$perceived_alt = alt$alt_avg
  #sanity_check_alt = describe(alt) #check for correct variables

    #AVGS FOR ALL GROUPS BY MOTIVE, PERSON, ACTION (ncol = 72)
    
      #AVG: altruism ratings - motive
      mtvdata = alt[,grep("m_", names(alt))] #get alt ratings of motives
        #ncol(mtvdata) #sanity check
      mtvdata = mtvdata %>% mutate(actC_avg_m_alt=rowMeans(mtvdata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_m_alt = mtvdata$actC_avg_m_alt #write to main df
  
      #AVG: altruism ratings - person
      psndata = alt[,grep("p_", names(alt))] #get alt ratings of persons
        #ncol(psndata) #sanity check
      psndata = psndata %>% mutate(actC_avg_p_alt=rowMeans(psndata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_p_alt = psndata$actC_avg_p_alt #write to main df
    
      #AVG: altruism ratings - action
      actdata = alt[,grep("a_", names(alt))] #get alt ratings of actions
      #ncol(actdata) #sanity check
      actdata = actdata %>% mutate(actC_avg_a_alt=rowMeans(actdata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_a_alt = actdata$actC_avg_a_alt #write to main df

    rm("mtvdata", "psndata", "actdata") #clean up workspace
  
    #AVGS FOR MOTIVES/OUTCOME GROUPS ONLY (ncol = 48)
    
      #AVG: altruism ratings - material 
      mdata = alt[,grep("_m", names(alt))] #get alt ratings of material motives/outcomes
      mdata = mdata[, -grep("actC", colnames(mdata))] #remove motive ratings from control group, which are picked via '_m'
        #ncol(mdata) #sanity check
      mdata = mdata %>% mutate(actMO_avg_m_alt=rowMeans(mdata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_m_alt = mdata$actMO_avg_m_alt #write to main df
    
      #AVG: altruism ratings - social
      sdata = alt[,grep("_s", names(alt))] #get alt ratings of social motives/outcomes
        #ncol(sdata) #sanity check
      sdata = sdata %>% mutate(actMO_avg_s_alt=rowMeans(sdata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_s_alt = sdata$actMO_avg_s_alt #write to main df
    
      #AVG: altruism ratings - emotional
      edata = alt[,grep("_e", names(alt))] #get alt ratings of emotional motives/outcomes
        #ncol(edata) #sanity check
      edata = edata %>% mutate(actMO_avg_e_alt=rowMeans(edata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_e_alt = edata$actMO_avg_e_alt #write to main df
    
      #AVG: altruism ratings - other-oriented
      odata = alt[,grep("_o", names(alt))] #get alt ratings of other-oriented motives/outcomes
        #ncol(odata) #sanity check
      odata = odata %>% mutate(actMO_avg_o_alt=rowMeans(odata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_o_alt = odata$actMO_avg_o_alt #write to main df
    
    rm("mdata", "sdata", "edata", "odata", "alt") #clean up workspace
    
#########################
  
#AVG: selfishness ratings
    self = df[,grep("Self", names(df))] #get all selfishness ratings 
    #DF should contain ncol = 216. Or N = 3 (DVs per V) x 8 (Vs) x 4 (orders) x 2 (cond: motive/outcome) + 3 (DVs per control V) x 8 (Vs)
      #ncol(self) #sanity check
    self = self %>% mutate(self_avg=rowMeans(self, na.rm = TRUE)) #create new column averaging across them
    data$perceived_self = self$self_avg
    #sanity_check_self = describe(self) #check for correct variables 

  
    #AVGS FOR ALL GROUPS BY MOTIVE, PERSON, ACTION (ncol = 72)
    
      #AVG: selfishness ratings - motive
      mtvdata = self[,grep("m_", names(self))] #get self ratings of motives
        #ncol(mtvdata) #sanity check
      mtvdata = mtvdata %>% mutate(actC_avg_m_self=rowMeans(mtvdata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_m_self = mtvdata$actC_avg_m_self #write to main df
    
      #AVG: selfishness ratings - person
      psndata = self[,grep("p_", names(self))] #get self ratings of persons
        #ncol(psndata) #sanity check
      psndata = psndata %>% mutate(actC_avg_p_self=rowMeans(psndata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_p_self = psndata$actC_avg_p_self #write to main df
    
      #AVG: selfishness ratings - action
      actdata = self[,grep("a_", names(self))] #get self ratings of actions
        #ncol(actdata) #sanity check
      actdata = actdata %>% mutate(actC_avg_a_self=rowMeans(actdata, na.rm = TRUE)) #create new column averaging across them
      data$actC_avg_a_self = actdata$actC_avg_a_self #write to main df
    
    rm("mtvdata", "psndata", "actdata") #clean up workspace
  
    #AVGS FOR MOTIVES/OUTCOME GROUPS ONLY (ncol = 48)
  
      #AVG: selfishness ratings - material
      mdata = self[,grep("_m", names(self))] #get self ratings of material motives/outcomes
      mdata = mdata[, -grep("actC", colnames(mdata))] #remove motive ratings from control group, which are picked via '_m' 
      #the above was not an issue for 'e', 's', or 'o'
        #ncol(mdata) #sanity check
      mdata = mdata %>% mutate(actMO_avg_m_self=rowMeans(mdata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_m_self = mdata$actMO_avg_m_self #write to main df
    
      #AVG: selfishness ratings - social
      sdata = self[,grep("_s", names(self))] #get self ratings of social motives/outcomes
        #ncol(sdata) #sanity check
      sdata = sdata %>% mutate(actMO_avg_s_self=rowMeans(sdata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_s_self = sdata$actMO_avg_s_self #write to main df
    
      #AVG: selfishness ratings - emotional
      edata = self[,grep("_e", names(self))] #get self ratings of emotional motives/outcomes
        #ncol(edata) #sanity check
      edata = edata %>% mutate(actMO_avg_e_self=rowMeans(edata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_e_self = edata$actMO_avg_e_self #write to main df
    
      #AVG: selfishness ratings - other-oriented
      odata = self[,grep("_o", names(self))] #get self ratings of other-oriented motives/outcomes
        #ncol(odata) #sanity check
      odata = odata %>% mutate(actMO_avg_o_self=rowMeans(odata, na.rm = TRUE)) #create new column averaging across them
      data$actMO_avg_o_self = odata$actMO_avg_o_self #write to main df
    
    rm("mdata", "sdata", "edata", "odata", "self") #clean up workspace
    
#Note: One belief item (variable name: self_belief1) that ranged from 1 to 5 (i.e., 1-2-3-4-5) was mistakenly 're-coded' in the Qualtrics' output as 1-3-4-5-6. The survey, as viewed by participants, displayed correctly. The code below fixes the output error:
  df$self_belief1[df$self_belief1 == "1"] <- "2"
  df$self_belief1 = as.numeric(df$self_belief1)
  df$self_belief1 = (df$self_belief1 - 1)
    
```

```{r exclusions, include=FALSE}

#create average reading time to exclude those who did not read the prosocial scenarios
  rt = df[,grep("rt", names(df))] #get variables containing time
  #ncol(rt) #should be 72. 8 (DVs per 2) x 1 (Cond: Control) + (8 (Vs) x 4 (orders) x 2 (cond: motive/outcome))
  rt = rt %>% mutate(rt_avg=rowMeans(rt, na.rm = TRUE)) #create new column called 'avg' averaging across them
  data$rt = rt$rt_avg
  rm("rt")
  data = data[ , !(names(data) %in% c("condition"))] #rm condition to avoid variable duplcating during merge
  df <- merge(df,data,by="id") #merge our two data frames
  rm("data")

  threshold = 1.5  # minimum RT required to read vignettes
  removedRT = subset(df, rt < threshold)  # Ps removed for falling below min avg RT
  data = subset(df, rt >= threshold)  # new dataset, with people below minimum RT removed
  rm("df")
  
#plyr::count(data$condition) # participants per condition
  # 1 = control
  # 2 = motive
  # 3 = outcome

```

```{r data reduction & validation,warning=FALSE, include=FALSE}

#internal validity
  validity = data[c("actC_avg_a_alt","actC_avg_a_self","actC_avg_m_alt",	"actC_avg_m_self","actC_avg_p_alt","actC_avg_p_self")]	
  # alpha(validity, keys=c("actC_avg_a_alt","-actC_avg_a_self","actC_avg_m_alt",	"-actC_avg_m_self","actC_avg_p_alt","-actC_avg_p_self"),
  #       cumulative=FALSE,
  #       title=NULL, max=10,na.rm = FALSE,
  #       check.keys=TRUE,n.iter=1,delete=TRUE)

#correlation between for ratings of altruism (and selfishness) for agent's action, agent's motive, and the agent.
  data_reduce_alt = validity[c(1,3,5)]
  reduce_corr_alt = cor(data_reduce_alt)
  round(reduce_corr_alt, 2)

  data_reduce_self = validity[c(2,4,6)]
  reduce_corr_self = cor(data_reduce_self)
  round(reduce_corr_self, 2)
  
#compute average altruism and selfishness ratings
  data$perceived_alt = (data$actC_avg_a_alt + data$actC_avg_m_alt + data$actC_avg_p_alt)/3
  data$perceived_self = (data$actC_avg_a_self + data$actC_avg_m_self + data$actC_avg_p_self)/3

#collapsing across altruism and selfishness ratings 

  #compute average perceived altruism collapsing across all ratings
    data$alt_comp = ((data$perceived_alt - data$perceived_self)/2)
    
  #compute average perceived altruism for each benefit-type
    data$alt_comp_e = ((data$actMO_avg_e_alt - data$actMO_avg_e_self)/2)
    data$alt_comp_m = ((data$actMO_avg_m_alt - data$actMO_avg_m_self)/2)
    data$alt_comp_o = ((data$actMO_avg_o_alt - data$actMO_avg_o_self)/2)
    data$alt_comp_s = ((data$actMO_avg_s_alt - data$actMO_avg_s_self)/2)
  
  #compute average perceived altruism collapsing across all ratings
    data$alt_comp = ((data$perceived_alt - data$perceived_self)/2)
    
```

```{r compute trait BETA / EC / PT, include=FALSE} 

#note: CRT computed manually

#composite score for trait BETA
keys.list <- list(beta=c("BETA_1","BETA_2","-BETA_3","-BETA_4","BETA_5","BETA_6","BETA_7","-BETA_8","-BETA_9","-BETA_10"))
beta <- scoreItems(keys.list,data)
#summary(beta)
#describe(beta$scores)
data$beta <- beta$scores #add BETA composite measure to dataset

#composite score for trait Empathic Concern (EC)
keys.list <- list(EC=c("iri2","iri4","iri9","-iri14","-iri18","iri20","iri22"))
ec <- scoreItems(keys.list,data,impute="none")
#summary(ec)
#describe(ec$scores)
data$ec <- ec$scores #add EC composite measure to dataset

#composite score for trait Perspective Taking (PT)
keys.list <- list(PT=c("-iri3","iri8","-iri11","iri15","iri21","iri25","iri28"))
pt <- scoreItems(keys.list,data,impute="none") #(scale rubric, dataset, ignore blanks)
#summary(pt)
#describe(pt$scores)
data$pt <- pt$scores #add PT composite measure to dataset

```

```{r main analyses1, include=FALSE}

#PROSOCIAL ACTION: do beliefs correlate with actions?

  #1. does BETA correlate with volunteering?
    data_psb = reduceFun(data, "proDV")#create subset of data, because not all Ps completed prosocial DV (N = 9)
    t1 = cor.test(data_psb$beta, data_psb$proDV) 
    tidy(t1)
    
  #2. does BETA correlate with volunteering, even after controlling for Empathic Concern and Perspective Taking
    control_vars <- c("ec","pt")
    control_df <- data_psb[control_vars]
    t2 = pcor.test(data_psb$beta, data_psb$proDV, control_df)
    tidy(t2)
    
```

```{r main analyses2, include=FALSE}

#PROSOCIAL INFERENCE: do beliefs correlate with inferences?
    
  #3. does BETA correlate with perceptions of altruism in the CONTROL condition?
    cond3_data <- subset(data, condition == "3") #subset data by condition
    #correlate BETA w/ perceived altruism and selfishness
    t3a = cor.test(cond3_data$beta, cond3_data$perceived_alt)
    t3b = cor.test(cond3_data$beta, cond3_data$perceived_self)
    tidy(t3a)
    tidy(t3b)

  #4. does BETA correlate with perceptions of altruism in the UNAMBIGUOUS condition?
    cond2_data <- subset(data, condition == "2") #subset data by condition
    #correlate BETA w/ perceived altruism and selfishness
    t4a = cor.test(cond2_data$beta, cond2_data$perceived_alt)
    t4b = cor.test(cond2_data$beta, cond2_data$perceived_self)
    tidy(t4a)
    tidy(t4b)

  #5. does BETA correlate with perceptions of altruism in the AMBIGUOUS condition?
    cond1_data <- subset(data, condition == "1") #subset data by condition
    #correlate BETA w/ perceived altruism and selfishness
    t5a = cor.test(cond1_data$beta, cond1_data$perceived_alt)
    t5b = cor.test(cond1_data$beta, cond1_data$perceived_self)
    tidy(t5a)
    tidy(t5b)
    
```

```{r main analyses3, include=FALSE}

#RELATION TO TRAIT MEASURES: do beliefs correlate with trait empathy or cognitive reflection?
   
  #6. does BETA correlate with empathic concern?
    t6 = cor.test(data$beta, data$ec)
    tidy(t6)

  #7. does BETA correlate with perspective taking?
    t7 = cor.test(data$beta, data$pt)
    tidy(t7)

  #8. does BETA correlate with cognitive reflection?
    t8 = cor.test(data$beta, data$CRT)
    tidy(t8)
    
```

```{r main analyses4, include=FALSE}
  
#BELIEFS ABOUT SELF AND OTHER: do beliefs in altruism reflect self-serving biases?
   
  #9. does BETA correlate CAPACITY beliefs for (a) self and (b) others?
    t9a = cor.test(data$beta, data$self_belief1)
    t9b = cor.test(data$beta, data$other_belief1)
    tidy(t9a)
    tidy(t9b)
    
  #10. does BETA correlate FREQUENCY beliefs for (a) self and (b) others?
    t10a = cor.test(data$beta, data$self_belief2)
    t10b = cor.test(data$beta, data$other_belief2)
    tidy(t10a)
    tidy(t10b)
    
  #11. do CAPACITY beliefs differ between self and others?
    t11 = t.test(data$self_belief1,data$other_belief1, paired=TRUE)
    t11d = cohensD(data$self_belief1,data$other_belief1) #obtain effect size
    tidy(t11)
    
  #12. do FREQUENCY beliefs differ between self and others?
    t12 = t.test(data$self_belief2,data$other_belief2, paired=TRUE)
    t12d = cohensD(data$self_belief2,data$other_belief2) #obtain effect size
    tidy(t12)
    
  #13. do individual differences between CAPACITY beliefs for self vs. other relate to BETA
    data$self_other_belief1_diff <- (data$self_belief1 - data$other_belief1) # compute diff. score for self/other capacity beliefs 
    t13 = cor.test(data$beta, data$self_other_belief1_diff)
    tidy(t13)
    
  #14. do individual differences between FREQUENCY beliefs for self vs. other relate to BETA
    data$self_other_belief2_diff <- (data$self_belief2 - data$other_belief2) # compute diff. score for self/other frequency beliefs
    t14 = cor.test(data$beta, data$self_other_belief2_diff)
    tidy(t14)

```
#####Study 2 - Results

(*M~BETA~* = `r rd(mean(data$beta),2)`, *SD~BETA~* = `r rd(sd(data$beta),2)`)

######PROSOCIAL ACTION: do beliefs correlate with actions?

  1. does BETA correlate with volunteering?
  
    (*r*(`r t1$par`) = `r rd(t1$e,2)`, *p* `r format_pval(t1$p.v)`, 95% CI [`r rd(t1$conf.int[1],2)`,`r rd(t1$conf.int[2],2)`])

  2. does BETA correlate with volunteering, even after controlling for Empathic Concern and Perspective Taking
  
    (*r*(274) = `r rd(t2$e,2)`, *p* `r format_pval(t2$p.v)`, 95% CI [.04,.27])
  
######PROSOCIAL INFERENCE: do beliefs correlate with inferences?
    
  3. does BETA correlate with perceptions of altruism in the CONTROL condition?
  
    (*r*(`r t3a$par`) = `r rd(t3a$e,2)`, *p* `r format_pval(t3a$p.v)`, 95% CI [`r rd(t3a$conf.int[1],2)`,`r rd(t3a$conf.int[2],2)`])

    (*r*(`r t3b$par`) = `r rd(t3b$e,2)`, *p* `r format_pval(t3b$p.v)`, 95% CI [`r rd(t3b$conf.int[1],2)`,`r rd(t3b$conf.int[2],2)`])

  4. does BETA correlate with perceptions of altruism in the UNAMBIGUOUS condition?
  
    (*r*(`r t4a$par`) = `r rd(t4a$e,2)`, *p* `r format_pval(t4a$p.v)`, 95% CI [`r rd(t4a$conf.int[1],2)`,`r rd(t4a$conf.int[2],2)`])

    (*r*(`r t4b$par`) = `r rd(t4b$e,2)`, *p* `r format_pval(t4b$p.v)`, 95% CI [`r rd(t4b$conf.int[1],2)`,`r rd(t4b$conf.int[2],2)`])

  5. does BETA correlate with perceptions of altruism in the AMBIGUOUS condition?
  
    (*r*(`r t5a$par`) = `r rd(t5a$e,2)`, *p* `r format_pval(t5a$p.v)`, 95% CI [`r rd(t5a$conf.int[1],2)`,`r rd(t5a$conf.int[2],2)`])
    
    (*r*(`r t5b$par`) = `r rd(t5b$e,2)`, *p* `r format_pval(t5b$p.v)`, 95% CI [`r rd(t5b$conf.int[1],2)`,`r rd(t5b$conf.int[2],2)`])
 
######RELATION TO TRAIT MEASURES: do beliefs correlate with trait empathy or cognitive reflection?
   
  6. does BETA correlate with empathic concern?
  
    (*r*(`r t6$par`) = `r rd(t6$e,2)`, *p* `r format_pval(t6$p.v)`, 95% CI [`r rd(t6$conf.int[1],2)`,`r rd(t6$conf.int[2],2)`])

  7. does BETA correlate with perspective taking?
  
    (*r*(`r t7$par`) = `r rd(t7$e,2)`, *p* `r format_pval(t7$p.v)`, 95% CI [`r rd(t7$conf.int[1],2)`,`r rd(t7$conf.int[2],2)`])

  8. does BETA correlate with cognitive reflection?
  
    (*r*(`r t8$par`) = `r rd(t8$e,2)`, *p* `r format_pval(t8$p.v)`, 95% CI [`r rd(t8$conf.int[1],2)`,`r rd(t8$conf.int[2],2)`])

######BELIEFS ABOUT SELF AND OTHER: do beliefs in altruism reflect self-serving biases?
   
  9. does BETA correlate CAPACITY beliefs for (a) self and (b) others?
  
    (self: *r*(`r t9a$par`) = `r rd(t9a$e,2)`, *p* `r format_pval(t9a$p.v)`, 95% CI [`r rd(t9a$conf.int[1],2)`,`r rd(t9a$conf.int[2],2)`]; others: *r*(`r t9b$par`) = `r rd(t9b$e,2)`, *p* `r format_pval(t9b$p.v)`, 95% CI [`r rd(t9b$conf.int[1],2)`,`r rd(t9b$conf.int[2],2)`])
    
  10. does BETA correlate FREQUENCY beliefs for (a) self and (b) others?
  
    (self: *r*(`r t10a$par`) = `r rd(t10a$e,2)`, *p* `r format_pval(t10a$p.v)`, 95% CI [`r rd(t10a$conf.int[1],2)`,`r rd(t10a$conf.int[2],2)`]; others: *r*(`r t10b$par`) = `r rd(t10b$e,2)`, *p* `r format_pval(t10b$p.v)`, 95% CI [`r rd(t10b$conf.int[1],2)`,`r rd(t10b$conf.int[2],2)`])
    
  11. do CAPACITY beliefs differ between self and others?
  
    (*M* = `r rd(mean(data$self_belief1),2)`, *SD* = `r rd(sd(data$self_belief1),2)`)
    (*M* = `r rd(mean(data$other_belief1),2)`, *SD* = `r rd(sd(data$other_belief1),2)`, *t*(`r t11$par`) = `r rd(t11$e,2)`, *p* `r format_pval(t11$p.v)`, 95% CI [`r rd(t11$conf.int[1],2)`,`r rd(t11$conf.int[2],2)`], d = `r rd(t11d,2)`)
    
  12. do FREQUENCY beliefs differ between self and others?
  
    (*M* = `r rd(mean(data$self_belief2),2)`, *SD* = `r rd(sd(data$self_belief2),2)`)
    (*M* = `r rd(mean(data$other_belief2),2)`, *SD* = `r rd(sd(data$other_belief2),2)`, *t*(`r t12$par`) = `r rd(t12$e,2)`, *p* `r format_pval(t12$p.v)`, 95% CI [`r rd(t12$conf.int[1],2)`,`r rd(t12$conf.int[2],2)`], d = `r rd(t12d,2)`)
    
  13. do individual differences between CAPACITY beliefs for self vs. other relate
  
    (*r*(`r t13$par`) = `r rd(t13$e,2)`, *p* `r format_pval(t13$p.v)`, 95% CI [`r rd(t13$conf.int[1],2)`,`r rd(t13$conf.int[2],2)`])
    
  14. do individual differences between FREQUENCY beliefs for self vs. other relate
  
    (*r*(`r t14$par`) = `r rd(t14$e,2)`, *p* `r format_pval(t14$p.v)`, 95% CI [`r rd(t14$conf.int[1],2)`,`r rd(t14$conf.int[2],2)`])

```{r Supplemental: correlations between BETA and each benefit type,echo=FALSE}


# Ambiguous Motive correlations
  supp_data_cond3 <- subset(data, condition == "3") #

  #correlation between BETA and perceptions of altruism and selfishness for actions involving a:
    #material benefit
    aM_m_a = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_m_alt) # altruism
    aM_m_s = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_m_self) # selfishness
    # tidy(aM_m_a)
    # tidy(aM_m_s)
    
    #social benefit
    aM_s_a = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_s_alt) # altruism 
    aM_s_s = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_s_self) # selfishness 
    # tidy(aM_s_a)
    # tidy(aM_s_s)
    
    #emotional benefit
    aM_e_a = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_e_alt) # altruism 
    aM_e_s = cor.test(supp_data_cond3$beta, supp_data_cond3$actMO_avg_e_self) # selfishness 
    # tidy(aM_e_a)
    # tidy(aM_e_s)


# Unambiguous Motive correlations
  supp_data_cond2 <- subset(data, condition == "2")

  #correlation between BETA and perceptions of altruism and selfishness for actions involving a: 
    #material motive
    uM_m_a = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_m_alt) # altruism 
    uM_m_s = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_m_self) # selfishness 
    # tidy(uM_m_a)
    # tidy(uM_m_s)
  
    #social motive
    uM_s_a = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_s_alt) # altruism
    uM_s_s = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_s_self) # selfishness
    # tidy(uM_s_a)
    # tidy(uM_s_s)
    
    #emotional motive
    uM_e_a = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_e_alt) # altruism
    uM_e_s = cor.test(supp_data_cond2$beta, supp_data_cond2$actMO_avg_e_self) # selfishness
    # tidy(uM_e_a)
    # tidy(uM_e_s)
    
```
Supplemental Correlational Analyses

Ambiguous motive

  material
  
    `r rd(aM_m_a$est,2)`   95% CI:`r rd(aM_m_a$conf.int[1:2],2)`   p`r format_pval(aM_m_a$p.v)`
    
    `r rd(aM_m_s$est,2)`   95% CI:`r rd(aM_m_s$conf.int[1:2],2)`   p`r format_pval(aM_m_s$p.v)`
    
  social
  
    `r rd(aM_s_a$est,2)`   95% CI:`r rd(aM_s_a$conf.int[1:2],2)`   p`r format_pval(aM_s_a$p.v)`
    
    `r rd(aM_s_s$est,2)`   95% CI:`r rd(aM_s_s$conf.int[1:2],2)`   p`r format_pval(aM_s_s$p.v)`
    
  emotional
  
    `r rd(aM_e_a$est,2)`   95% CI:`r rd(aM_e_a$conf.int[1:2],2)`   p`r format_pval(aM_e_a$p.v)`
    
    `r rd(aM_e_s$est,2)`   95% CI:`r rd(aM_e_s$conf.int[1:2],2)`   p`r format_pval(aM_e_s$p.v)`
    

Unambiguous motive

  material
  
    `r rd(uM_m_a$est,2)`   95% CI:`r rd(uM_m_a$conf.int[1:2],2)`   p`r format_pval(uM_m_a$p.v)`
    
    `r rd(uM_m_s$est,2)`   95% CI:`r rd(uM_m_s$conf.int[1:2],2)`   p`r format_pval(uM_m_s$p.v)`
    
  social
  
    `r rd(uM_s_a$est,2)`   95% CI:`r rd(uM_s_a$conf.int[1:2],2)`   p`r format_pval(uM_s_a$p.v)`
    
    `r rd(uM_s_s$est,2)`   95% CI:`r rd(uM_s_s$conf.int[1:2],2)`   p`r format_pval(uM_s_s$p.v)`
    
  emotional
  
    `r rd(uM_e_a$est,2)`   95% CI:`r rd(uM_e_a$conf.int[1:2],2)`   p`r format_pval(uM_e_a$p.v)`
    
    `r rd(uM_e_s$est,2)`   95% CI:`r rd(uM_e_s$conf.int[1:2],2)`   p`r format_pval(uM_e_s$p.v)`
    
    
```{r s2_fig1,echo=FALSE}

#setup pdf output
  # pdf(file = "~/Box Sync/GitHub/belief_altMotives/s2_fig1.pdf",
  # width = 3.5,
  # height = 3)

ggplot(data=data, aes(data$beta)) +
  geom_histogram(aes(y =..density..),
                 alpha=.5,
                 bins = 14,
                 position = 'stack', 
                 stat = 'bin',
                 color="black",
                 fill="grey")+
  geom_density()+theme_classic()+
  xlab("belief in altruistic motivation")
  
#save output
 # dev.off()
```
 
```{r s2_fig2,echo=FALSE}

#setup pdf output 
#   pdf(file = "~/Box Sync/GitHub/belief_altMotives/s2_fig2.pdf",
#   width = 6, # The width of the plot in inches
#   height = 3) # The height of the plot in inches

plot3 = data %>% dplyr::select(perceived_alt,perceived_self, beta, condition)
  plot3 = gather(plot3, "selfOther", "perception",1:2)

  plot3$condition <- factor(plot3$condition,
                          levels = c("1","2","3"),
                          labels = c("no information", "unambiguous", "ambiguous"))
  
  plot3$selfOther <- factor(plot3$selfOther,
                          levels = c("perceived_alt","perceived_self"),
                          labels = c("altruistic", "selfish"))
  
ggplot(plot3,aes(beta,perception,color=condition))+
  xlab("belief in altruistic motivation")+
  geom_point()+
  facet_grid(selfOther~condition,switch = "y" )+ #switch = "y" to change label position
  geom_smooth(method = "lm", se = FALSE)+
  theme_minimal()

#save output
 # dev.off()

```

