---
title: "belief_AltMotives - study 1"
author: Ryan Carlson
output: html_document
---
```{r install/load packages,include=FALSE}

library("plyr") # plyr for aggregate data
library("rstudioapi")
library("ggplot2") #for plotting
library("ggm") # for partial correlations
library("ppcor") # " "
library("psych") # for trait measures
library("RVAideMemoire") #spearman bootstrapped CIs
library("weights") # for displaying APA style stats (e.g. "p = .01"")
library("broom")

```

```{r set directory, read in data set, include=FALSE}

#Set working directory to the location of this R file (note: the dataset should be in the same folder)
  # curr_dir <- getActiveDocumentContext()$path # get path to currently open R file
  # setwd(dirname(curr_dir)) # set the working directory to curr_dirr
  # #print(getwd()) # print directory
  # rm("curr_dir")

#Read dataset
  data <- read.csv('bAM_s1_data.csv') 
  
```

```{r knit functions,echo=FALSE, include=FALSE}
  
#formatting p-values for APA
format_pval <- function(x){
  if (x < .001) return(paste('<', '.001'))
  if (x > .1) return(paste('=', rd(x, 2)))
  paste('=', rd(x, 3))   # 3 = no. of digits to round p value to if p < .001 
}

```

```{r compute trait BETA and Altruism, include=FALSE}

#composite score for Belief in the Existence of True Altruism (BETA)
  keys.list <- list(beta=c("BETA_1","BETA_2","-BETA_3","-BETA_4","BETA_5","BETA_6","BETA_7","-BETA_8","-BETA_9","-BETA_10"))
  beta <- scoreItems(keys.list,data)
  beta$alpha
  data$beta <- beta$scores #add BETA composite measure to dataset

#composite score for trait altruism
  keys.list <- list(altruism=c("Altruism_1","Altruism_2","Altruism_3","Altruism_4","Altruism_5","Altruism_6","Altruism_7","Altruism_8","Altruism_9","Altruism_10","Altruism_11","Altruism_12","Altruism_13","Altruism_14","Altruism_15","Altruism_16","Altruism_17","Altruism_18","Altruism_19","Altruism_20"))
  altruism <- scoreItems(keys.list,data)
  altruism$alpha
  data$altruism <- altruism$scores #add Altruism composite measure to dataset
  
```

```{r main analyses, include=FALSE}

#1. does BETA correlate with trait prosociality
    t1 = cor.test(data$beta, data$altruism)
    tidy(t1)

#2. does BETA correlate with hypothetical giving
    t2 = cor.test(data$beta, data$give_hypo)
    tidy(t2)

#3. does BETA correlate with real giving
    t3 = cor.test(data$beta, data$give_real)
    tidy(t3)

#4a. does BETA correlate with hypothetical giving, even after controlling for trait prosociality
    t4a = pcor.test(data$beta, data$give_hypo, data$altruism)
    tidy(t4a)
    
#4a. does BETA correlate with real giving, even after controlling for trait prosociality
    t4b = pcor.test(data$beta, data$give_real, data$altruism)
    tidy(t4b)

```
#####Study 1 - Results

(*M~BETA~* = `r rd(mean(data$beta),2)`, *SD~BETA~* = `r rd(sd(data$beta),2)`)

  1. does BETA correlate with trait prosociality

    (*r*(`r t1$par`) = `r rd(t1$e,2)`, *p* `r format_pval(t1$p.v)`, 95% confidence interval (CI) [`r rd(t1$conf.int[1],2)`,`r rd(t1$conf.int[2],2)`])

  2. does BETA correlate with hypothetical giving

    (*r*(`r t2$par`) = `r rd(t2$e,2)`, *p* `r format_pval(t2$p.v)`, 95% CI [`r rd(t2$conf.int[1],2)`,`r rd(t2$conf.int[2],2)`])

  3. does BETA correlate with real giving

    (*r*(`r t3$par`) = `r rd(t3$e,2)`, *p* `r format_pval(t3$p.v)`, 95% CI [`r rd(t3$conf.int[1],2)`,`r rd(t3$conf.int[2],2)`])

  4. does BETA correlate with (a) hypothetical giving and (b) real giving, even after controlling for trait prosociality

    (*r*(`r t4a$par`) = `r rd(t4a$e,2)`, *p* `r format_pval(t4a$p.v)`, 95% CI [`r rd(t4a$conf.int[1],2)`,`r rd(t4a$conf.int[2],2)`])
 
    (*r*(`r t4b$par`) = `r rd(t4b$e,2)`, *p* `r format_pval(t4b$p.v)`, 95% CI [`r rd(t4b$conf.int[1],2)`,`r rd(t4b$conf.int[2],2)`])    
    

```{r s1_fig1,echo=FALSE}

#setup pdf output
  # pdf(file = "~/Box Sync/GitHub/belief_altMotives/s1_fig1.pdf",
  # width = 3.5,
  # height = 3)

ggplot(data=data, aes(data$beta)) +
  geom_histogram(aes(y =..density..),
                 alpha=.5,
                 bins = 14,
                 position = 'stack', 
                 stat = 'bin',
                 color="black",
                 fill="grey")+
  geom_density()+theme_classic()+
  xlab("belief in altruistic motivation")
  
#save output
  # dev.off()
```
 